%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Wireless Software Developer} % Job title
    {STMicroelectronics (STM)} % Organization
    {Waterloo, Ontario} % Location
    {Sept. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added support to an existing LTE NB \& MTC stack. Aided in debugging efforts, communicating with stack teams such as L1, PDCP, RLC, and MAC.}
        \item {Facilitated debugging efforts, effectively communicating with stack teams, including L1, PDCP, RLC, and MAC).}
        \item {Diagnosed and resolved stack issues using Amarisoft and Rohde \& Schwarz CMW wireless communication conformance testing equipment.}
        \item {Authored innovative tools, such as a Python tool named asngen, which generated a lightweight C translation layer from the 36.331 specification to replace the existing encoder/decoders. It enabled a decrease of read-only data by 148KB (48\%) compared to the existing implementation.}
        \item {Built and maintained lab machines equipt with FPGAs, ASICs, Amarisoft, and Rohde \& Schwarz equipment, ensuring a robust test environment.}
        \item {Assisted the ZigBee, Thread, and BLE Application teams in developing quality customer apps, demonstrating teamwork and customer focus.}
        \item {Communicated effectively with stack teams, including ZigBee APS, ZigBee NWK, and MAC 802.15.4, to aid in debugging efforts.}
        % \item {Generated and presented solutions to a larger group of developers, contributing to continuous quality improvements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Camera Software \& Embedded Firmware Developer} % Job title
    {Labforge Inc.} % Organization
    {Waterloo, Ontario} % Location
    {May 2020 - Sept. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programmed neural network model structures in PyTorch using publications for reference, demonstrating research and implementation skills.}
        \item {Trained models for object detection in Python/PyTorch, such as Resnet-18, Resnet-50, and EfficientDet, using both public and private datasets.}
        \item {Created private datasets for training models for object detection, showcasing initiative and data management skills.}
        \item {Designed and programmed innovative approaches to object re-identification and tracking in C/C++ and Python, achieving fast results.}
        \item {Improved inertial sensor code bases in C/C++ and managed sensor processes as Unix systemd daemons on stereo cameras.}
        \item {Collaborated with another software developer to create a reliable C/C++ state estimation engine for stereo camera tracking, demonstrating teamwork and technical collaboration. The product was presented to the Royal Canadian Air Force (posted on YouTube).}
        \item {Worked with another software developer to create robust C/C++ camera calibration and simulation software.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern Advanced Researcher \& Embedded Firmware Developer} % Job title
    {Northern Digital Inc.} % Organization
    {Waterloo, Ontario} % Location
    {May 2018 - Sept. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and programmed an embedded handheld device with multiple sensors to fuse with Polaris Vega infrared camera tracking data, showcasing innovation and technical skills.}
        \item {Collaborated with a Masters researcher to develop various data fusion algorithms (Vector, Quaternion, Pose estimation) in C++ and Python.}
        \item {Worked with another software developer to create a fast C/C++ sensor data simulation software.}
        \item {Partnered with another software developer to create a C/C++ and Python graphical viewer of real-data (replayed) and simulated data.}
        \item {Developed low-level firmware drivers for virtual reality hand remotes including IMUs, ADCs, DACs, FLASH, UART, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
...

%---------------------------------------------------------
  % \cventry
  %   {Co-op Safety Critical Systems Researcher (McSCert) \& Teaching Assistant (Department of Computing and Software)} % Job title
  %   {McMaster University} % Organization
  %   {Hamilton, Ontario} % Location
  %   {May - Dec. 2015 \& May - Sept. 2017} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Collaborated with a team of software engineers to develop and test a prototype pacemaker using a Freescale K64F, a custom PCB shield, and Matlab Simulink, demonstrating teamwork and technical skills.}
  %        % \item {Organized and conducted programming labs for first-year Computer Science and Engineering students, showcasing leadership and teaching abilities.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  % \cventry
  %   {Software Developer \& Shop Employee} % Job title
  %   {Emnor Mechanical Inc.} % Organization
  %   {Hamilton, Ontario} % Location
  %   {May - Sept. 2015 \& May - Sept. 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Demonstrated good organization skills by developing a Python inventory management software for the company warehouse.}
  %       \item {Improved mechanical design skills by reverse engineering damaged parts and producing CAD drawings using the Faro Arm.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------

\end{cventries}
